Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-09 arxiv/experiments.tex
section 4 polish

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
	\caption{Validating Example \ref{ex_same_cov} in the same covariates case. Our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d$ and sample size $n$ settings. The noise variance $\sigma^2$ is $1/4$.}
	\label{fig_same_cov}
\end{figure}

@@

We show that our asymptotic estimates match extremely well with empirical prediction losses in modest dimensions.
This study complements our high-dimensional asymptotic results whose error term vanishes when $p$ is sufficiently large.
We simulate the settings of the three examples in Section \ref{sec_same} and \ref{sec_diff} in dimension $p = 200$.

\paragraph{The same covariates case.}
First, we study the setting of Example \ref{ex_same_cov}.
Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task sample from $400$ to $4000$.
For all the parameter settings, we can estimate the empirical loss accurately using our results.
We also observe a trend where the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
Our result explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
Indeed, we observe a crossover point between hard parameter sharing and STL.
Finally, by looking horizontally at the same level of prediction loss, we observe that hard parameter sharing requires 3x less samples per-task than STL.

\paragraph{The different covariates case.}
Second, we show how varying sample ratio affects hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
Figure \ref{fig_size} shows task two's prediction loss as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
Again, our estimates are fairly accurate compared to the empirical losses.
We consider a larger sample size regime here where task two consists of $70,000$ samples and task one's sample size varies from $10,000$ to $56,000$.
We observe that as we increase the sample ratio, task two's prediction loss decreases intially but increases above the initial loss level.
Our result explains this trend since the task-specific variance $d^2 = 0.08$ is greater than task two's prediction loss, which is $\sigma^2 = 0.3^2$ times $p / (n_2 - p)$.
%We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.

Finally, we show that varying covariate shift affects hard parameter sharing in the setting of Example \ref{ex_covshift}.
Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
Recall that $\lambda$ measures the severity of covariate shift -- a higher $\lambda$ means more covariate shift.
Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.
The noise variance $\sigma^2$ is $1/4$.
%Covariate shift: We set $\kappa = 1$ and $d = 0$.
%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).

@@

\begin{figure}[!t]
%		\begin{subfigure}[b]{0.32\textwidth}
%		\centering
%		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
%		\caption{Sample efficiency}
%		\label{fig_model_shift}
%	\end{subfigure}\hfill
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/sample_ratio.eps}
		\caption{Example \ref{ex_sample_ratio}}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
		\caption{Example \ref{ex_covshift}}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in the different covariates case.
	In both experiments, our estimated loss (solid line) matches with the empirical loss (dotted line) accurately.
	In Figure \ref{fig_size}, we discover an interesting phenomenon by fixing task two's sample size and increasing task one's sample size.
	We observe that task two's prediction loss decreases initially before increasing again, and our result shows (provably) that this phenomenon occurs due to different bias-variance tradeoffs as the sample ratio increases.
	In Figure \ref{fig_covariate}, we show how covariate shift affects hard parameter sharing. We observe that when task two's sample size is greater than that of task one, covariate shift increases the prediction loss. Otherwise, covariate shift actually decreases the prediction loss (surprisingly).
	.}
	\label{fig_model_shift_phasetrans}
\end{figure}

@@

Our results and their implications are all in the high-dimensional linear regression setting.
How well do they extend to other settings?
In this section, we conduct further studies on a text classification task, for predicting whether the sentiment of a sentence is positive or negative.
We use six datasets including a review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, a opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
%The question is to predict positive or negative sentiment expressed in the text.
We use an embedding layer with GloVe embeddings \cite{pennington2014glove} followed by an LSTM, MLP or CNN layer proposed by~\citet{lei2018simple}.\footnote{For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings. For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings.}

@@

\paragraph{Sample ratio.}
In Figure \ref{fig_ab_data}, we observe that for multiple task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
On the $y$-axis, we plot task two's prediction accuracy using HPS, subtracted by its STL prediction accuracy.
%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
We fix task one's sample size as $1000$ and increase task two's number of samples from $100$ to $3000$.

Next, we propose a natural progressive training schedule for finding the optimal sample ratio.
Our training schedule is motivated by Corollary \ref{cor_MTL_loss}, which shows that as we increase the sample ratio, the prediction loss always decreases first and then increases.
%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
\begin{itemize}
	\item We divide the source task data into $S$ batches.
	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
\end{itemize}

@@

%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
%\squishlist
%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
%TREC is less similar to MR because the task is about question types.
%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
Our results show that progressive training requires less computation compared to a baseline round-robin training schedule, without sacrificing accuracy.
First, we show that our proposed progressive training schedule (can help mitigate negative transfer for predicting a particular target task.
Over all $15$ pairs from the sentiment analysis tasks, we find that progressive training requires only $45\%$ of the computational cost to achieve the same test accuracy on the target task, compared to HPS trained using round-robin.
Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
%\textbf{Improving transfer learning training efficiency.}
%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
Second, we show the progressive training schedule applies to multiple tasks as well.
Over all six sentiment analysis tasks, incremental training requires less than $35\%$ of the computational cost compared to baseline MTL training, while achieving the same accuracy averaged over all six tasks.
%As a further validation, excluding TREC, we observe similar comparative results.
%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

\begin{figure}%[!t]
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\vspace{0pt}
		\includegraphics[width=0.6\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
		\caption{HPS vs. STL}
		\label{fig_ab_data}
	\end{subfigure}\hfill
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\vspace{0pt}
		\includegraphics[width=0.6\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{HPS vs. covariance alignment}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{Comparing hard parameter sharing to single-task learning (STL) and a covariance alignment approach proposed by \citet{WZR20}.
	In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS. }
	\label{fig_text}
%	\begin{minipage}[t]{0.4\textwidth}
%		\centering
%		\vspace{0pt}
%		\begin{tabular}{c c c}
%		\toprule
		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
		% Sentiment\\ analysis\end{center}\end{minipage}} \\
%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
		% \cmidrule(lr){2-3}
%		& all tasks & w/o TREC \\
%		\midrule
%		{\bf MLP}  & 31\% & 29\% \\
%		{\bf LSTM} & 35\% & 34\% \\
%		{\bf CNN}  & 30\% & 28\% \\
%		\bottomrule
%		\end{tabular}
%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
%		\label{tab:taskonomy}
%	\end{minipage}
\end{figure}

@@

\paragraph{Covariate shift.}
Recall from Example \ref{ex_covshift} that when the sample ratio increases, covariate shift worsens.
Hence when the sample ratio increases, we expect procedures that aim at correcting covariate shift to provide more significant gains.
To this end, we study a covariance alignment procedure proposed in \citet{WZR20}, which is designed for correcting covariate shift.
The idea is to add an alignment module between the input and the shared module $B$.
This new module is then trained together with $B$ and the output layers -- more details on the procedure and the implementation can be found in that paper.
%We validate our insight on this procedure in the experiments.
%We implement the covariance alignment procedure following \cite{WZR20}.

In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
We average the results over all 15 task pairs.
The result shows that as the source samples increases, covariance alignment improves more over HPS.
We fix task two's sample size at $1,000$ and increase task one's sample size from $1,000$ to $3,000$.

>>>>

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
	\caption{Validating Example \ref{ex_same_cov} in the same covariates case: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d$ and sample size $n$ settings. The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
	\label{fig_same_cov}
\end{figure}

@@

We demonstrate the accuracy of our results via some empirical results.
While our theory is asymptotic (with error terms that vanish when $p$ is sufficiently large), we observe that they are accurate in a modest dimension of $p = 200$.

\paragraph{The same covariates case.}
First, we study the setting of Example \ref{ex_same_cov}.
Figure \ref{fig_same_cov} shows the average prediction loss as we increase the number of samples per-task sample from $400$ to $4000$.
For all the parameter settings, our results estimate the empirical losses accurately.
We also observe a trend where the average prediction loss increases as we increase $d$ from $0.1$ to $0.2$.
Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
Indeed, we observe a crossover point between hard parameter sharing and STL.
Finally, looking horizontally at the same prediction loss level, we find that hard parameter sharing requires 3x fewer samples per-task than STL.

\paragraph{The different covariates case.}
Second, we show how varying sample ratio impacts hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
Figure \ref{fig_size} shows task two's prediction loss as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
Again, our estimates are reasonably accurate compared to the empirical losses.
We consider a regime where task two consists of $80,000$ samples, and task one's sample size vary from $8,000$ to $56,000$.
We observe that as we increase the sample ratio, task two's prediction loss decreases initially but increases above the initial loss level.
Our work explains this trend since the task-specific variance $d^2 = 0.08$ is higher than task two's prediction loss, which is $\sigma^2 = 0.3^2$ times $p / (n_2 - p)$.
%We use $\rho_2 = 500$ and vary $\rho_1$ from $50$ to $800$ for sample sizes.

Finally, we show how varying covariate shift impacts hard parameter sharing in the setting of Example \ref{ex_covshift}.
Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
Recall that $\lambda$ measures the severity of covariate shifts -- a higher $\lambda$ means more covariate shift.
Our estimates match the empirical losses accurately, and indeed we observe the dichotomy in Example \ref{ex_covshift}.
The noise variance $\sigma^2$ is $1/4$.
%Covariate shift: We set $\kappa = 1$ and $d = 0$.
%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).

@@

\begin{figure}[!t]
%		\begin{subfigure}[b]{0.32\textwidth}
%		\centering
%		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
%		\caption{Sample efficiency}
%		\label{fig_model_shift}
%	\end{subfigure}\hfill
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_c2_400.eps}
		\caption{Example \ref{ex_sample_ratio}}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
		\caption{Example \ref{ex_covshift}}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in the different covariates case:
	in both experiments, our estimated losses (solid line) match the empirical losses (dotted line) accurately.
	In Figure \ref{fig_size}, we discover an interesting phenomenon by fixing task two's sample size and increasing task one's sample size.
	We observe that task two's prediction loss decreases initially before increasing again. Our result shows (provably) that this phenomenon occurs due to different bias-variance tradeoffs as the sample ratio increases.
	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing.
	Having covariate shifts increases task two's prediction loss when task two's sample size is larger than task one. Otherwise, having covariate shifts decreases task two's prediction loss (surprisingly).}
	\label{fig_model_shift_phasetrans}
\end{figure}

@@

Our results and their implications are all in the high-dimensional linear regression setting.
How well do they extend to other settings?
In this section, we conduct further studies on a text classification task, for predicting whether  a sentence has a positive or negative sentiment.
Our datasets include a review sentiment dataset (MR) \cite{pang2005seeing}, a sentence subjectivity dataset (SUBJ) \cite{pang2004sentimental}, a customer reviews dataset (CR) \cite{hu2004mining}, a question type dataset (TREC) \cite{li2002learning}, an opinion polarity dataset (MPQA) \cite{wiebe2005annotating}, and the Stanford sentiment treebank (SST) dataset \cite{socher2013recursive}.
%The question is to predict positive or negative sentiment expressed in the text.
Our model consists of a word embedding layer with GloVe embeddings \cite{pennington2014glove} followed by a long-short term memory (LSTM) or a multi-layer perception (MLP) layer \citet{lei2018simple}.\footnote{For multi-layer perception (MLP), we apply an average pooling layer over the word embeddings. For LSTM and CNN, we add a shared feature representation layer on top of the word embeddings.}

@@

\paragraph{Sample ratio.}
In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
We fix task one's sample size at $1000$ and increase task two's sample size from $100$ to $3000$.
These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops.
%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
Concretely,
\begin{itemize}
	\item we divide the source task data into $S$ batches.
	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
\end{itemize}
For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate until reaching the optimal sample ratio.
The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.

@@

%We fill in the details of the experimental procedure used for the results in Figure \ref{fig_ablation}.
%\squishlist
%	\item Task similarity: We select a similar and a dissimilar source task compared to the target task using domain knowledge.
%First pair: the customer review dataset (CR) , which predicts whether a review is positive or negative, is more similar to SST (sentiment treebank) than MPQA (question type).
%Second pair: SST is more similar to MR since they both concern about positive or negative opinions expressed the text.
%TREC is less similar to MR because the task is about question types.
%Third pair: MPQA (opinion polarity) is more similar to TREC (question type)
We evaluate the progressive training procedure on the six text classification datasets.
First, we conduct multi-task training over all $15$ pairs from the six datasets.
We find that adding task one's samples progressive requires only $45\%$ of the computational cost to achieve the same test accuracy for task two than standard round-robin training schedules.
%Our insight is that since adding more samples from the source task does not always help, we can improve efficiency by adding source samples \textit{progressively} during training.
%\textbf{Improving transfer learning training efficiency.}
%We show that Algorithm \ref{alg_inc_train} also applies to transfer learning settings.
%Compared to fine-tuning the source model on the target task, we show that our proposed method reduces the computional cost by \alert{$xx\%$}, without sacrificing accuracy.
Second, we conduct multi-task training on all six datasets.
We find that adding samples progressively from all datasets requires less than $35\%$ of the computational cost to achieve the same test accuracy averaged over the six datasets than standard round-robin training schedules.
%As a further validation, excluding TREC, we observe similar comparative results.
%The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
%We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

\begin{figure}%[!t]
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\vspace{0pt}
		\includegraphics[width=0.6\textwidth]{figures/ratio_norm_3_pairs_lstm.pdf}
		\caption{HPS vs. STL}
		\label{fig_ab_data}
	\end{subfigure}\hfill
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\vspace{0pt}
		\includegraphics[width=0.6\textwidth]{figures/ratio_alignment_norm_diff_all.pdf}
		\caption{HPS vs. covariance alignment}
		\label{fig_ab_cov}
	\end{subfigure}
	\caption{Comparing hard parameter sharing (HPS) to single-task learning (STL) and a covariance alignment approach proposed by \citet{WZR20}:
	In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually -- a phenomenon similar  to Figure \ref{fig_size}.
	In Figure \ref{fig_ab_cov}, we observe that as task one's sample size increases, covariance alignment improves more over HPS.}
	\label{fig_text}
%	\begin{minipage}[t]{0.4\textwidth}
%		\centering
%		\vspace{0pt}
%		\begin{tabular}{c c c}
%		\toprule
		% \multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.2in}\begin{center}
		% Sentiment\\ analysis\end{center}\end{minipage}} \\
%		\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\bf Sentiment analysis} \\
		% \cmidrule(lr){2-3}
%		& all tasks & w/o TREC \\
%		\midrule
%		{\bf MLP}  & 31\% & 29\% \\
%		{\bf LSTM} & 35\% & 34\% \\
%		{\bf CNN}  & 30\% & 28\% \\
%		\bottomrule
%		\end{tabular}
%		\captionof{table}{Finding the best sample ratio via a progressive training schedule.}
%		\label{tab:taskonomy}
%	\end{minipage}
\end{figure}

@@

\paragraph{Covariate shift.}
Recall from Example \ref{ex_covshift} that having covariate shifts worsens the variance (hence the loss) of hard parameter sharing when the sample ratio increases.
This highlights the need for correcting covariate shifts when the sample ratio rises.
To this end, we study a covariance alignment procedure proposed in \citet{WZR20}, designed to correct covariate shifts.
The idea is to add an alignment module between the input and the shared module $B$.
This module is then trained together with $B$ and the output layers. We refer to \citet{WZR20} for more details about the procedure and the implementation.
%We validate our insight on this procedure in the experiments.
%We implement the covariance alignment procedure following \cite{WZR20}.

We conduct multi-task training on all $15$ task pairs from the six datasets.
In Figure \ref{fig_ab_cov}, we measure the performance gains from performing covariance alignment vs. HPS.
To get a robust comparison, we average the improvements over the 15 task pairs.
The result shows that as the sample ratio increases, performing covariance alignment provides more significant gains over HPS.
We fix task two's sample size at $1,000$, and increase task one's sample size from $1,000$ to $3,000$.
